---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(sparseR)
```

# Implementing ranked sparsity methods with sparseR

[![codecov](https://codecov.io/gh/petersonR/sparseR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/petersonR/sparseR)
[![R-CMD-check](https://github.com/petersonR/sparseR/workflows/R-CMD-check/badge.svg)](https://github.com/petersonR/sparseR/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/sparseR)](https://CRAN.R-project.org/package=sparseR)

## What is ranked sparsity?

The ranked sparsity methods such as the sparsity-ranked lasso (SRL) have been developed for model selection and estimation in the presence of interactions and polynomials (Peterson & Cavanaugh 2022)[https://doi.org/10.1007/s10182-021-00431-7]. The main idea is that an algorithm should be more skeptical of higher-order polynomials and interactions a priori compared to main effects, by a predetermined amount.

## Package overview

The `sparseR` package implements ranked-sparsity-based versions of the lasso, elastic net, MCP, and SCAD. We also provide a (preliminary) version of an sparsity-ranked extension to Bayesian Information Criterion (and corresponding stepwise approaches)

Additionally, `sparseR` has many features designed to streamline dealing with interaction terms and polynomials, including functions for variable pre-processing, variable selection, post-selection inference, and post-fit model visualization under ranked sparsity.

## Installation 

```{r gh-installation, eval = FALSE}

## Via GitHub: 
# install.packages("devtools")
devtools::install_github("petersonR/sparseR")

# or via CRAN
install.packages("sparseR")
```

## Example

```{r, eval = FALSE}
library(sparseR)
```

```{r example}
data(iris)
set.seed(1321)

srl <- sparseR(Sepal.Width ~ ., data = iris, k = 1, seed = 1)
srl
```

For more examples and a closer look at how to use this package, check out the [package website](https://petersonr.github.io/sparseR/). 

Many thanks to the authors and maintainers of [`ncvreg`](https://github.com/pbreheny/ncvreg) and [`recipes`](https://recipes.tidymodels.org/). 
