---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(sparseR)
```

# Implementing ranked sparsity methods with sparseR

[![codecov](https://codecov.io/gh/petersonR/sparseR/branch/main/graph/badge.svg)](https://codecov.io/gh/petersonR/sparseR)
[![R-CMD-check](https://github.com/petersonR/sparseR/workflows/R-CMD-check/badge.svg)](https://github.com/petersonR/sparseR/actions)

## Overview

The `sparseR` package implements the following ranked sparsity methods:

1) Sparsity-ranked lasso
2) Sparsity-ranked MCP
3) Sparsity-ranked SCAD
4) Ranked Bayesian Information Criterion (and corresponding stepwise approaches)

Additionally, `sparseR` has many features designed to streamline dealing with interaction terms and polynomials, including functions for variable pre-processing, variable selection, post-selection inference, and post-fit model visualization under ranked sparsity.

The package is currently in beta phase (version 0.0.1), with plans for a stable release to CRAN in February 2022. A publication detailing ranked sparsity principles is currently under review, and available upon request. 

## Installation 

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("petersonR/sparseR")
```

## Example

```{r, eval = FALSE}
library(sparseR)
```

```{r example}
data(iris)
set.seed(1321)

srl <- sparseR(Sepal.Width ~ ., data = iris, k = 1, seed = 1)
srl
```

For more examples and a closer look, check out the [package website](https://petersonr.github.io/sparseR/). 
